\documentclass[PaulGanssle-Thesis.tex]{subfiles}
\begin{document}

\begin{acknowledgements}
I owe my thanks to many people who have dedicated their time to my personal and professional development during the course of my graduate work. First of all, Alex Pines and all my colleagues in the Pines Lab during my time there, all of whom seem to have conspired to make it a pleasant, fun working and academic environment.

I tend to think through problems best by discussion, and so I'm sincerely grateful to the many people who have volunteered their time and energy as counterpoints, collaborators and mentors. This includes most everyone in the Pines lab during my time at Berkeley, and many members of Dmitry Budker's lab as well. In particular, Scott ``Kremice'' Seltzer\footnote{While his given name is ``Scott Jeffrey Seltzer'', he prefers to be called Kremice, pronounced /\textipa{krEmIs}/. It is also appropriate to call him ``K-Man'', ``Kremdog Millionaire'' or ``The Kremtastic Voyage''.} and Micah Ledbetter provided invaluable feedback on the design, operation and troubleshooting of alkali vapor-cell magnetometers, among many, many other topics. My early research in the Pines Lab on J-coupling and para-hydrogen induced polarization (mostly not covered in this document) was carried out alongside Thomas Theis and Gwendal Kervern, both of whom were integral to development as an NMR scientist; Mark Butler should also be added to this list, as I relied heavily on his expertise, analytical mind and supreme patience as I was learning the fundamental concepts of NMR and spin dynamics. To the list of intellectual mentors and advisors I should also add Chang Shin, who provided me advice on electronics and electrical engineering that shapes my fundamental approach to circuit design to this day.

I would also like to specifically thank Dmitry Budker for his always sage advice on many subjects both scientific and professional, he was always gracious with his time and attention and always provided extremely useful feedback at every stage of the process from initial design to publication. Similarly, I owe much to Vik Bajaj, who served as a day-to-day advisor and mentor in the Pines Lab and who significantly shaped my scientific and professional development during this time. 

Finally, I would like to specifically acknowledge the contributions that Hyun ``Doug'' Shin made to this work during his undergraduate career at Berkeley. He was capable and dedicated, and a brilliant machinist --- it took great restraint for me to not delegate all my machine work to Doug, as I knew that even though it would probably not help his career development much to spend so much time in the machine shop I also knew that he would probably do an even better job than I would if I gave him the task.

\end{acknowledgements}

\end{document}